---
title: "RAG with VectrixDB Backend"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RAG with VectrixDB Backend}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette shows how to use `VectrixDB` as the retrieval backend in
`RAGFlowChainR`.

## 1) Install and load packages

```{r}
# install.packages("remotes")
# remotes::install_github("knowusuboaky/vectrixdb-r")

library(RAGFlowChainR)
library(VectrixDB)
```

## 2) Create a VectrixDB collection and add documents

```{r}
store_path <- tempfile("vectrix_store_")
dir.create(store_path, recursive = TRUE, showWarnings = FALSE)

db <- VectrixDB::vectrix_open(name = "default", path = store_path)

db$add(
  texts = c(
    "R is widely used for statistics and data analysis.",
    "VectrixDB is a lightweight vector database implemented in R.",
    "RAGFlowChainR can retrieve context before calling the LLM."
  ),
  metadata = list(
    list(source = "doc_1"),
    list(source = "doc_2"),
    list(source = "doc_3")
  )
)

db$close()
```

## 3) Create a RAG chain with method = "VectrixDB"

```{r}
mock_llm <- function(prompt) {
  "This is a mock answer from the LLM."
}

rag_chain <- create_rag_chain(
  llm = mock_llm,
  vector_database_directory = store_path,
  method = "VectrixDB",
  use_web_search = FALSE
)
```

## 4) Query the chain

```{r}
result <- rag_chain$invoke("What is VectrixDB?")

result$answer
result$documents
```

## 5) Cleanup

```{r}
rag_chain$disconnect()
unlink(store_path, recursive = TRUE)
```

## Notes

- `create_rag_chain(method = "VectrixDB")` requires package `VectrixDB`.
- If `VectrixDB` is not installed, `create_rag_chain()` raises a clear error with installation steps.
- `vector_database_directory` can point to a Vectrix root directory, collection directory, or collection name.
